%-------------------------
% Resume in Latex
% Author : Matheus Hoffmann
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{ragged2e}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    {\Huge \scshape Matheus Hoffmann Brito} \\ \vspace{1pt}
    Rio de Janeiro, Brazil \\ \vspace{1pt}
    \small \raisebox{-0.1\height}\faPhone\ +55 (21) 99718-7508 ~ \href{mailto:mmatheushb@hotmail.com}{\raisebox{-0.2\height}\faEnvelope\  \underline{mmatheushb@hotmail.com}} ~ 
    \href{https://linkedin.com/in/matheus-hoffmann}{\raisebox{-0.2\height}\faLinkedin\ \underline{matheus-hoffmann}}  ~
    \href{https://github.com/matheus-hoffmann}{\raisebox{-0.2\height}\faGithub\ \underline{matheus-hoffmann}}
    \vspace{-8pt}
\end{center}


%-----------EDUCATION-----------
\section{Education}
\resumeSubHeadingListStart
\resumeSubheading
{Pontifical Catholic University of Rio de Janeiro (PUC-Rio)}{Feb. 2020 -- Aug. 2022}
{Master of Science in Mechanical Engineering}{Rio de Janeiro, RJ}
\resumeSubheading
{Pontifical Catholic University of Rio de Janeiro (PUC-Rio)}{Feb. 2014 -- Dec. 2018}
{Bachelor of Science in Mechanical Engineering}{Rio de Janeiro, RJ}
\resumeSubHeadingListEnd


%-----------PROFESSIONAL EXPERIENCE-----------
\section{Professional Experience}
\resumeSubHeadingListStart
\justifying

\resumeSubheading
{\href{https://www.nttdata.com/global/en/}{NTT DATA}}{Feb. 2023 -- Present}
{Generative AI Team Leader}{Remote - Rio de Janeiro, RJ}

As a technical leader, I am responsible for the design and development of generative AI solutions to empower our clients in meeting their demands. My role encompasses understanding business needs, crafting technical and commercial proposals, and estimating development and operational costs. Among the projects I have worked on, the following initiatives stand out:
\resumeItemListStart
\resumeItem{Implementation of a Generative AI Hub for a client: Development of a Generative AI Hub for a client aimed at consolidating best practices, training employees, and structuring the necessary service infrastructure to support new initiatives.}
\resumeItem{Creation and development of a chatbot for corporate HR activities: Implementation of an Agentic Chatbot integrated with Microsoft Teams that allowed employees to consult company policies, schedule and cancel vacations, and create and register a job offer on the employment platform (Gupy). All communication with this chatbot can be conducted via text messages or audio.}
\resumeItem{Creation and development of a corporate chatbot: Implementation of an Agentic Chatbot that queries corporate documents, searches for information in different SQL tables on Databricks. This intelligent system generates dynamic graphs to visualize tabular data, simplifying analysis and interpretation. Integrated into a custom web interface and Microsoft Teams, the chatbot allows users to communicate seamlessly via text messages or audio.}
\resumeItem{Development of a Speech Analytics solution for call centers: Creation of a Speech Analytics solution to enhance operational performance in call centers. The solution transcribes and extracts information from phone calls, helping to identify and classify the root cause of issues reported by customers. This application led to a 60\% SLA reduction in overall operation.}
\resumeItem{Creation of a bug assistant: Development of a Generative AI solution to increase operational efficiency in handling bugs across different company systems, using historical event records and specific operational rules for each system as a basis. This application led to a 35\% SLA reduction in overall operation.}
\resumeItem{Content creation for marketing campaigns: Development of a tool to generate textual and visual content for marketing campaigns based on specified characteristics.}
\resumeItemListEnd

\resumeSubheading
{\href{https://www.ctis.com.br}{CTIS | SONDA Group}}{Oct. 2021 -- Jan. 2023}
{Machine Learning Engineer}{Remote - Rio de Janeiro, RJ}
\resumeItemListStart
\resumeItem{Develop 3D convolutional neural network (3D CNN) architectures to perform medical image segmentation using TensorFlow and Keras's open-source libraries in a High-Performance Computing (HPC) environment.}
\resumeItem{Development of algorithms to guarantee the random and balanced division of the dataset composed of numerical and categorical parameters.}
\resumeItemListEnd

\resumeSubheading
{\href{https://www.tecgraf.puc-rio.br}{Tecgraf}}{Mar. 2019 -- Sep. 2021}
{Software Engineer}{Rio de Janeiro, RJ}
\resumeItemListStart
\resumeItem{Developed a predictive model using machine learning techniques from scarce data, along with pre and post-processing routines in Python and Shell scripts to manage batch runs of OpenFOAM simulations.}
\resumeItem{Developed a middleware to connect the REFPROP API with a C++ GUI library.}
\resumeItemListEnd

\resumeSubheading
{\href{http://yieldcontrol.com.br}{Yield Control Soluções em Energia S/A}}{Mar. 2018 -- Dec. 2018}
{Mechanical Engineer Intern}{Rio de Janeiro, RJ}
\resumeItemListStart
\resumeItem{Customization and optimization of the HVAC system, creating an operational profile that reduces costs and increases the system’s performance.}
\resumeItemListEnd

\resumeSubHeadingListEnd
\vspace{-16pt}


%-----------PUBLICATIONS---------------
\section{Publications}
\justifying
\resumeItemListStart
\resumeItem{\href{https://www.maxwell.vrac.puc-rio.br/61107/61107.PDF}{BRITO, M. H., Predicting dry gas seals reliability with machine learning techniques developed from scarce data, Master Thesis, (Rio de Janeiro, Brazil), 2022.}}

\resumeItem{\href{https://biblioteca.ibp.org.br/riooilegas/pt-BR/search/40243?exp=}{KASSAR, B. B. M.; MARQUES, R. G. C.; JUNIOR, H. B. B.; BRITO, M. H., Improving operational equipment reliability with CFD analysis: case study of dry gas seal, Rio Oil and Gas Expo and Conference, (Rio de Janeiro, Brazil), 2020.}}
\resumeItemListEnd


%-----------OTHER EXPERIENCE-----------
\section{Other Relevant Experience}
\resumeSubHeadingListStart
\justifying

\resumeSubheading
{Co-advise undergraduate students final projects}{Mar. 2019 -- Jun. 2021}
{Co-advisor}{Rio de Janeiro, RJ}
\resumeItemListStart
\resumeItem{Co-advised four final project studies on off-road vehicle’s brake, powertrain and suspension components topology optimization.}
\resumeItemListEnd

\resumeSubheading
{Baja Rio competition volunteering}{Nov. 2018 -- Aug. 2021}
{Committee}{Rio de Janeiro, RJ}
\resumeItemListStart
\resumeItem{Creation of the mentoring project, whose objective was to guarantee the technical evolution of Baja teams in Rio de Janeiro.}
\resumeItemListEnd

\resumeSubHeadingListEnd
\vspace{-16pt}

%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
\justifying
\small{\item{
\textbf{Programming Languages}{: Python, C++, C, Bash, SQL, MATLAB/Simulink.} \\
\textbf{Cloud Platforms}{: Azure, GCP, AWS.} \\
\textbf{Frameworks/Libraries}{: LangChain, LangGraph, CrewAI, Scikit-learn, TensorFlow, Keras.} \\
\textbf{Relevant Coursework}{: Machine Learning, Signal Processing, System Identification, Design of Experiments, Control of Systems, Numerical Optimization.} \\
\textbf{Others skills}{: Software Documentation, Object-oriented Programming, Event-driven Programming, Multilingual communication (Portuguese, English and Spanish (Certificate DELE - B2)).} \\
}}
\end{itemize}
\vspace{-16pt}

\end{document}
